Inference of proto-neutron star properties from gravitational-wave data in core-collapse supernovae

### 2021-02-02 referee_answers.txt

We thank the refereee for his/her supportive comments and provide
answers below.

----------------------------------------------------------------------
Report of the Referee -- DY12631/Bizouard
----------------------------------------------------------------------

1. As far as I can tell, the model assumes that the GW signal is
dominated by g-modes originating from the PNS, which is consistent
with results reported from recent CCSN simulations from some groups.
However, other groups, using three-dimensional simulations, attribute
the dominant component to f- and g-modes (Radice et al. (2019), ApJL,
876, L9) or p- and g-modes (Mezzacappa et al. (2020), Phys. Rev. D,
102, 023027). Can the authors comment on this. In particular, discuss
the possible impact on model predictions if the signal is hybrid in
nature.

A. We believe that a discussion of the nature of the modes is out of 
the scope of this paper. The nature of the mode visible in the time-frequency
evolution do not affect our analysis. The only assumption is that there is 
an excited mode (whatever its nature) whose frequency scales with the properties 
of the proto-neutron star following a universal relation. It is true that
the ratio used (M/R^2) is inspired by the presence of a g-mode and we and this
interpretation is discussed in our previous work. In Torres-Forne 
et al. Phys. Rev. Lett. 123, 051102 (2019) fits to the various modes (f, p, 
and g) that appear in the spectrograms of a number of CCSN simulations were 
discussed, and universal relations for the frequency evolution were proposed.
The best fit for the dominant feature found in all simulations was that 
corresponding to what was identified as a g-mode. We agree with the referee 
that uncertainties remain on the actual nature of the various modes identified 
in simulations performed by various groups. Further work is certainly necessary 
to clarify this issue, not only regarding three-dimensional simulations but also 
regarding the development of improved perturbative models for mode identification 
that incorporate 3D effects and rotation in a more accurate way that existing 
approaches. The current uncertainty in the identification of the modes at work 
during the evolution of a PNS is of no importance for the message that this
paper conveys.

@@

2. Most analysis of GW signals is based on two-dimensional models, and
the test set used in the present study is also comprised of 2D
simulations. Recent comparisons of signals from 2D and 3D simulations
show that the signal amplitude from 2D simulations is considerably
higher than in 3D simulations (e.g., Andresen et al. (2017), MNRAS,
468, 2032; see also Mezzacappa et al. 2020). I would like the authors
to comment on this, and its potential impact on the results presented
in the present paper. Would this just lower the upper limit of the
detectability distance? Are there other crucial differences between
signals from 2D and 3D simulations (e.g., the low frequency signal
from the spiral SASI mode) that could compromise the accuracy of the
model derived here? Please discuss this.

A. The referee is correct. A reduction in the amplitude of the GW signal
would reduce the detectability distance. Regarding the model we put forward
in this paper, it is indeed possible that the physical effects that only 
appear in 3D CCSN simulations could alter the relationship between the 
mode frequencies and the PNS properties that we have used in this paper. 
Sotani & Takiwaki 2020a,b, compared simulations with different dimensionality 
(1D, 2D and 3D) and found no differences for a limited set of models (this
is mentioned in our work in the introduction). This work, thus, is far from 
providing the final word on the detectability prospects of GW signals from PNS 
evolution, but it certainly serves the purpose of offering a promising 
proof-of-concept and a framework upon which to build a better model. We plan 
to use data from 3D simulations to improve our model and to study the differences 
in the relationships among 1D, 2D and 3D simulations. We have added a comment on 
this important caveat in the conclusion.

"Moreover, we have used 2D CCSN simulations
that are known to produce higher amplitude GW signals
than 3D CCSN simulations [48, 49]. This fact and the
low frequency standing accretion shock instability that
appears only in 3D simulations may reduce further the
performance of the method."

@@

We have rewritten the corresponding paragraph to clarify this.

"For the mean of the ratios $r_i$ , the cubic model has the
best fitting amongst polynomials of lower degrees, and
for the mean of the log standard deviation $\rm log \sigma_i$ , the
quadratic model has the best fit compared to a polynomial
of degree one. The models were compared according
to the Akaike information criterion. The estimated coefficients
are given in Table II and the data and fit of the
final model including 95\% confidence bands are displayed
in Figure 1."

6. What do the red circles in Figure 1 represent? Is it a scatter plot
of the results from all 1D simulations taken together? Specifically,
since there obviously is more than 18 circles, how often is data from
each simulation sampled to generate the circles in Figure 1? Please
clarify this. Perhaps using a unique color for each model would help
clarify (but I do not demand this).

A: Each of the 18 1D simulations is providing data points r_i that are
plotted as function of f_i. Each simulation has between 100 and 300
points. All of them are plotted on Figure 1. We share with the referee 
a figure where each EOS is singled out with color (ratio_allmass.png).

### 2021-02-02 methods.tex
minor revision

\textcolor{red}{For the mean of the ratios $r_i$, the cubic model has the best fitting amongst polynomials of lower degrees, and for the mean of the log standard deviation $\log\sigma_i$, the quadratic model has the best fit compared to a polynomial of degree one.  The models were compared according to the Akaike information criterion.  The estimated coefficients are given in Table \ref{tab:model} and the data and fit of the final model including 95\% confidence bands are displayed in
Figure~\ref{fig:LMVAR}.}

>>>>

\textcolor{red}{For the mean of the ratios $r_i$, the cubic model has the best fitting amongst polynomials of lower degrees, and for the mean of the log standard deviation $\log\sigma_i$, the quadratic model has the best fit compared to a polynomial of degree one. The models were compared according to the Akaike information criterion.  The estimated coefficients are given in Table \ref{tab:model} and the data and fit of the final model, including 95\% confidence bands, are displayed in Figure~\ref{fig:LMVAR}.}
